### 2016-10-05 robust-software.tex
Print the version number

\item
Remind people that a program should print its version number in all of its output,
particularly debugging traces.

@@

The version of your software should be easily available, both when
supplying \texttt{-\/-version} or \texttt{-v} on the command line as
well as in the results. The software version should be printed to the
same location as all of the other parameters (see Rule 4).

>>>>

@@

The version of your software should be easily available, both when
supplying \texttt{-\/-version} or \texttt{-v} on the command line as
well as in the results. The software version should be printed to the
same location as all of the other parameters (see Rule 4).  It should
also be included in all of the program's output, particularly debugging
traces: if someone needs help, it's important that they be able to tell
whoever's helping them which version of the software they're using.
